The Impact of Alternation

### 2017-05-10 draft.tex
ok

@@

  \State $\Lambda(n_i) \leftarrow \Lambda(n_i) \wedge I_i$
  \Comment{strenghten the label of $n_i$}
  \label{ln:close-refine}

  \State $\Call{Close}{n_i}$
  \label{ln:refine-end}

@@

\begin{algorithmic}[1]
\Function{Close}{$x$}

@@

\State {\bf return}

@@

@@

The execution of Algorithm \ref{alg:impact} consists of three
phases\footnote{These phases correspond to the \textsc{Close},
  \textsc{Refine} and \textsc{Expand} procedures from the original
  description of \impact~\cite{mcmillan06}.}: \emph{close},
\emph{refine} and \emph{expand}. When a node $n$ is removed from the
worklist, it is first closed (line \ref{ln:close-worklist}) by finding
a lexicographically bigger node $m$ such that $\Lambda(n) \models
\Lambda(m)$, if one exists, and adding $(n,m)$ to $\lhd$. As in
Algorithm \ref{alg:predabs}, the intuition is that all successors of
$n$ are covered by the successors of $m$, thus for any feasible
counterexample that can be discovered from $n$ there exists a feasible
counterexample stemming in $m$, and we do not need to process $n$
further.

If $n$ has not been covered in the close phase, we check if it is the
endpoint of a counterexample candidate, which can only be the case
when the replacement set $R(n)$ contains at least one final state
(line \ref{ln:cex}). Observe that, if $u$ is the label of the path
from $\rootNode$ to $n$, then $\Accept{\A}(u)$ is satisfiable only if
it contains a (positive occurrence of) a final state. The
counterexample is feasible if and only if $\mu(n)$ is satisfiable, in
which case a model of $\mu(n)$ is obtained and a word $w \in L(\A)$
returned. Otherwise, the counterexample is spurious and the procedure
enters the refinement phase (lines \ref{ln:refine-begin} -
\ref{ln:refine-end}). The interpolant for $\mu(n)$ is used to
strenghten the labels of all the ancestors of $n$, by conjoining the
formulae of the interpolant to the existing labels. In this process,
some node might become eligible for coverage, therefore we attempt to
close each ancestor of $n$ that is impacted by the refinement (line
\ref{ln:close-refine}). Observe that, in this case the call to
$\Call{Close}{}$ must uncover each node which is covered by a
successor of $n$ (line \ref{ln:close-uncover} in the $\Call{Close}{}$
procedure). This is required because, due to the over-approximation of
the sets of reachable configurations, the covering relation is not
transitive, as explained in \cite{mcmillan06}.

>>>>

  \State let $b$ be $\false$

@@

  \State $\Lambda(n_i) \leftarrow \Lambda(n_i) \wedge I_i$
  \Comment{strenghten the label of $n_i$}

  \If{$\neg b$}

  \State $b \leftarrow \Call{Close}{n_i}$
  \label{ln:refine-end}

@@

\begin{algorithmic}[1]
\Function{Close}{$x$} {\bf returns} $\Bool$

@@

\State {\bf return} $\true$

@@

\State {\bf return} $\false$

@@

The execution of Algorithm \ref{alg:impact} consists of three
phases\footnote{These phases correspond to the \textsc{Close},
  \textsc{Refine} and \textsc{Expand} procedures from the original
  description of \impact~\cite{mcmillan06}.}: \emph{close},
\emph{refine} and \emph{expand}. When a node $n$ is removed from the
worklist, it is first closed (line \ref{ln:close-worklist}) by finding
a lexicographically bigger node $m$ such that $\Lambda(n) \models
\Lambda(m)$, if one exists, and adding $(n,m)$ to $\lhd$. As in
Algorithm \ref{alg:predabs}, the intuition is that for any feasible
counterexample that can be discovered from $n$ there exists a feasible
counterexample stemming in $m$, thus we do not need to process $n$
further.

If $n$ has not been previously covered at line
\ref{ln:close-worklist}, we check if it is the endpoint of a
counterexample candidate, which can only be the case when the
replacement set $R(n)$ contains at least one final state (line
\ref{ln:cex}). Observe that, if $u$ is the label of the path from
$\rootNode$ to $n$, then $\Accept{\A}(u)$ is satisfiable only if it
contains a (positive occurrence of) a final state. The counterexample
is moreover feasible iff $\mu(n)$ is satisfiable, in which case a model of
$\mu(n)$ is obtained and a word $w \in L(\A)$ returned.

Otherwise, the counterexample is spurious and the procedure enters the
refinement phase (lines \ref{ln:refine-begin} -
\ref{ln:refine-end}). The interpolant for $\mu(n)$ is used to
strenghten the labels of all the ancestors of $n$, by conjoining the
formulae of the interpolant to the existing labels. In this process,
some node might become eligible for coverage, therefore we attempt to
close each ancestor of $n$ that is impacted by the refinement (line
\ref{ln:refine-end}). Observe that, in this case the call to
$\Call{Close}{}$ must uncover each node which is covered by a
successor of $n$ (line \ref{ln:close-uncover} in the $\Call{Close}{}$
procedure). This is required because, due to the over-approximation of
the sets of reachable configurations, the covering relation is not
transitive, as explained in \cite{mcmillan06}.
